\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\pagenumbering{gobble}
\setcounter{secnumdepth}{0}
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\vspace{0.15em}\titlerule]
\titlespacing*{\section}{0pt}{0.85em}{0.35em}
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt}

% Avoid word breaks/hyphenation; allow a bit of stretch to reduce overfull lines.
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=1em

\newcommand{\cvsubheading}[2]{\textbf{#1}\hfill #2\\}

\begin{document}

\begin{center}
{\LARGE \textbf{Dr. Shruti Shah (PT)}}\\
Physiotherapist (BPT, India)\\
\small \href{mailto:shrutishah201103@gmail.com}{shrutishah201103@gmail.com} \textbar\ +91 8468980847 \textbar\ \href{https://www.linkedin.com/in/dr-shruti-shah-pt-}{linkedin.com/in/dr-shruti-shah-pt-}\normalsize
\end{center}

\section*{Profile}
BPT-trained physiotherapist with clinical experience across multi-specialty hospital rotations and a supervised spine-clinic internship. Skilled in evidence-based rehabilitation planning for musculoskeletal, sports, and post-operative care, with manual therapy and patient education experience. Research background includes a completed 6-month experimental study, an STS fellowship project, and a clinical case study, plus national conference presentations.

\section*{Education}
\cvsubheading{Bachelor of Physiotherapy (BPT), Dr. D. Y. Patil College of Physiotherapy, Pune}{2021--2025}
GPA: 7.25/10 (First Class)\\
Rotatory Internship: Aug 2025 -- Mar 2026 (1092 hours)

\textbf{Relevant Coursework}\\
Prerequisite-aligned coursework: Human Anatomy I \& II; Human Physiology; General Chemistry;\\
Pathology \& Microbiology; Exercise Sciences and Exercise Therapy; Biomechanics;\\
Research Methodology \& Biostatistics (Statistics); Psychology;\\
English \& Communication Skills (oral communication).\\
Additional clinical coursework: Orthopedics; Neurology; Cardiorespiratory and General Conditions.\\
Electives: Physiotherapy in Manual Therapy (semester 7),\\
Physiotherapy in Sports (semester 8).

\textbf{Academic highlights:}
\begin{itemize}
  \item Case presentations: 5 cases across musculoskeletal, neurosciences, cardiopulmonary and general conditions, and community-based rehabilitation.
  \item Journal club presentations: 2.
\end{itemize}

\section*{Clinical Experience}
\cvsubheading{Clinical Intern, Dr. D. Y. Patil Hospital, Pune}{Aug 2025 -- Mar 2026}
\begin{itemize}
  \item Rotational clinical services across orthopedics, neurology, cardiopulmonary, pediatrics, medicine and surgery,\\
  Women's Health, and ICU in a high-volume, multi-specialty hospital.
  \item Community-based physiotherapy interventions at PCMC Divyang Bhavan Foundation, Amrutvel Old Age Home (Pimpri),\\
  and Dr. D. Y. Patil Rural Health Training Centre (Alandi).
  \item Multidisciplinary rotations at Dr. D. Y. Patil College of Ayurveda and Research Center and Dr. D. Y. Patil Homeopathic Medical College and Research Center.
  \item Musculoskeletal and sports rehab: evaluation and treatment of acute and sub-acute injuries;\\
  individualized rehab programs; progression based on response and goals.
  \item Manual therapy: joint mobilization grades I to IV and soft tissue techniques to improve pain,\\
  mechanics, and range of motion.
  \item Neurological rehab: neurodevelopmental treatment (NDT)\\
  and proprioceptive neuromuscular facilitation (PNF) for\\
  stroke and spinal cord injury to improve motor control and function.
  \item Cardiopulmonary rehab:\\
  chest physiotherapy, breathing exercises,\\
  and early mobilization for post-cardiac surgery patients.
  \item Sports performance and acute injury management\\
  with return-to-sport planning.
\end{itemize}

\cvsubheading{Intern (Observation Hours with Licensed PTs), Capri Spine Clinic, Pune}{Jul 2024 -- Jan 2025}
\begin{itemize}
  \item Assisted in comprehensive musculoskeletal assessment, clinical reasoning,\\
  and formulation of physiotherapy diagnoses for spine and peripheral joint conditions under licensed PT supervision.
  \item Implemented individualized rehabilitation programs focusing on pain reduction, mobility restoration,\\
  postural correction, and functional independence.
  \item Applied manual therapy techniques, including soft tissue mobilization and joint mobilizations, to improve spinal and\\
  peripheral joint function.
  \item Educated patients on posture correction, ergonomics, activity modification, and home exercise programs, improving\\
  adherence and long-term outcomes.
  \item Supervised observation hours with licensed PTs: 6:00 PM to 9:00 PM,\\
  6 days per week (approx. 468 hours).
\end{itemize}

\section*{Research Projects}
\begin{itemize}
  \item Immediate Effects of Lumbopelvic Rotational Exercise on Hamstring Flexibility and Running Gait Velocity in\\
  Recreational Runners -- An Experimental Study. 6-month research project (completed).
  \item Effects of Grade V Spinal Mobilization on Segmental Spinal Range of Motion and Flexibility in Asymptomatic Individuals.\\
  STS Fellowship project, Dr. D. Y. Patil College of Physiotherapy, Pune.\\
  Role: study design, screening and assessment, data collection, statistical analysis, and interpretation.
  \item Effects of Physiotherapy and Management of Foville Syndrome. Clinical case study. Role: clinical evaluation, intervention planning, outcome monitoring, and documentation.
\end{itemize}

\section*{Conference Presentations and Awards}
\begin{itemize}
  \item First Place, Scientific Paper Presentation, PHYSIO-DROME National Physiotherapy Conference,\\
  Dr. D. Y. Patil College of Physiotherapy, Pune -- ``A Case Study on Foville Syndrome.''
  \item First Place, Undergraduate Scientific Paper Presentation, Physio-Drome 2026 International Summit,\\
  Dr. D. Y. Patil College of Physiotherapy, Pune --\\
  ``Immediate Effects of Lumbopelvic Rotational Exercise on Hamstring Flexibility\\
  and Running Gait Velocity in Recreational Runners -- An Experimental Study.''\\
  Awarded 1st place among ~600 student research presentations.
  \item First Prize, Outstanding Research Paper Presentation (UG Category),\\
  Electrocon-24 National Electrotherapy Conference,\\
  Maharashtra Institute of Physiotherapy, Latur --\\
  ``Functional and Clinical Outcomes of Matrix Rhythm Therapy in Frozen Shoulder:\\
  A Detailed Case Report.''
\end{itemize}

\section*{Certifications}
\begin{itemize}
  \item Certified Kinesio Taping Practitioner (CKTP).
  \item Certified in Nerve Conduction Studies (NCS).
\end{itemize}

\section*{Volunteer Sports Physiotherapy}
\begin{itemize}
  \item Apla Pune Marathon (2024--25) -- On-field physiotherapist; acute injury assessment, taping, cryotherapy,\\
  and recovery guidance.
  \item Indian Army Soldierathon/CME (Nov 2025) -- On-field physiotherapist; emergency first aid, triage,\\
  and return-to-activity support.
  \item Bombay Sappers Soldierathon (Jun 2025) -- On-field physiotherapist; acute injury care, basic life support,\\
  and recovery protocols.
  \item Maharashtra State Football Association U-14 Tournament (Aug 2024) -- On-field physiotherapist; injury assessment\\
  and return-to-play coordination.
\end{itemize}

\section*{Leadership and Campus Activities}
\textbf{Student Council Roles:}
\begin{itemize}
  \item General Secretary (2024--25)
  \item Co-Sports Secretary (2023--24)
  \item Hospitality Committee Lead (2022--23)
  \item Student Council Member (2021--22)
\end{itemize}

\textbf{Selected activities:}
\begin{itemize}
  \item Initiated weekend plogging and volunteered as an English teacher for underprivileged children.
  \item Helped organize on-campus concerts, coordinating with artists and managers.
\end{itemize}

\end{document}
